---
title: "Case_Study"
author: "Rachel"
date: "11/2/2021"
output: github_document
---
```{r setup, include=FALSE}
library(tidyverse)
library(leaflet)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

library(p8105.datasets)
library(tidyverse)
```

## Load a dataset 

```{r}
data("nyc_airbnb")
```

* How many rentals are there? Of what type? In what places? 
* Is price correlated with review score? 
* Which neighborhood is most popular? Most expensive? 
* Which neighborhood has the highest review? 
* Is availability related to price? 
* Is room type related to neighborhood? 
* IS length of stay related to neighborhood group (borough)? 

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(borough = neighbourhood_group)
  
```

Let's try to count thinsg: 

```{r}
nyc_airbnb %>% 
  janitor::tabyl(borough, room_type)
```

```{r}
nyc_airbnb %>% 
  count(borough, room_type) %>% 
  pivot_wider(
    names_from = room_type, 
    values_from = n)
```

Let's look price and room type...
```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price)) +
  geom_point() + 
  facet_grid(. ~ room_type)
```

*Type 2 
```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price)) +
  geom_boxplot()
```

Price and neighborhood 

```{r}
nyc_airbnb %>% 
  group_by(neighbourhood) %>% 
  summarize(mean_price = mean(price, na.rm = TRUE))
```
```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  group_by(neighbourhood) %>% 
  summarize(mean_price = mean(price, na.rm = TRUE)) %>% 
  
  arrange(mean_price)
```

```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  group_by(neighbourhood) %>% 
  summarize(mean_price = mean(price, na.rm = TRUE)) %>% 
  arrange(mean_price)

nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot() +
  coord_flip()
```


```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  group_by(neighbourhood) %>% 
  summarize(mean_price = mean(price, na.rm = TRUE)) %>% 
  arrange(mean_price)

nyc_airbnb %>% 
  filter(borough == "Manhattan",
         price <= 1000) %>% 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot() +
  coord_flip()
```


```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  group_by(neighbourhood) %>% 
  summarize(mean_price = mean(price, na.rm = TRUE)) %>% 
  arrange(mean_price)

nyc_airbnb %>% 
  filter(borough == "Manhattan",
         price <= 1000) %>% 
  mutate(neighbourhood = 
           fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot() +
  coord_flip()
```

```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  group_by(neighbourhood) %>% 
  summarize(mean_price = mean(price, na.rm = TRUE)) %>% 
  arrange(mean_price)

nyc_airbnb %>% 
  filter(borough == "Manhattan",
         price <= 1000) %>% 
  mutate(neighbourhood = 
           fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot() +
  coord_flip() + 
  facet_grid(. ~ room_type)
```


Price vs. Location 

```{r}
nyc_airbnb %>% 
  sample_n(5000) %>% 
  ggplot(aes(x = lat, y = long, color = price)) + 
  geom_point(alpha = .5)
```
## Retry leaflet

```{r, eval = FALSE}
nyc_airbnb %>% 
  filter(price < 500) %>% 
  sample_n(1000) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addMarkers(~lat, ~long)
```

* Tiles
```{r, eval = FALSE}
nyc_airbnb %>% 
  filter(price < 500) %>% 
  sample_n(1000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 

  addMarkers(~lat, ~long)
```

* markers 
```{r, eval = FALSE}
nyc_airbnb %>% 
  filter(price < 500) %>% 
  sample_n(1000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lat, ~long, radius = 1)
```

* Colors 
```{r, eval = FALSE}
pal = 
  colorNumeric("viridis", NULL)
nyc_airbnb %>% 
  filter(price < 500) %>% 
  sample_n(1000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
addCircleMarkers(~lat, ~long, radius = 1, ~pal(price)) 
```

```{r}
pal = colorNumeric("viridis", NULL)

nyc_airbnb %>% 
  mutate(
    labels = str_c("<b>", price, "</b><br>", stars)
  ) %>% view


nyc_airbnb %>% 
  filter(price < 500) %>% 
  sample_n(1000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
addCircleMarkers(~lat, ~long, radius = 1, ~pal(price)) 
```

